### 2023-11-17 scripts/manuscript.qmd
Initial commit. Data imported, portions of method section written, paper outlined.

---
title: "manuscript"
format: pdf
editor: visual
author: "Leah Peterson, Alexus Rock, and Ben Pfingston"
---

```{r}
#| include: FALSE
library(tidyverse)
library(here)
library(rio)
library(psych)
```

```{r}
#| echo: FALSE
communication <- import(here("data", "communication"))
```

# Introduction

(Joe asked us about the specific hypotheses guiding our paper. My suggestion is that we are curious about relations between suspicion and young adults' privacy perceptions, as well as gender differences in young adults suspicion and privacy perceptions)

# Method

## Sample

104 participants were recruited primarily through an undergraduate student body located in Minnesota. The participation criteria required that participants be at least 18 years old and have interacted with a teacher in a school setting. Demographic information, such as age, gender identity, and ethnic-racial identity was also collected.

## Measures

To measure different aspects of student-teacher trust interactions, items were modified from Ledbetter and Vik’s (2012) Parental Privacy Invasions Scale (PPIS) and Levine and McCornack’s (1991) Suspicion Scale.

### Modified Parental Privacy Invasions Scale
Eleven items were adapted from the Parental Privacy Invasions Scale to reflect teacher, rather than parental, interactions. Each item was measured on a five-point Likert scale, ranging from 0 to 4, with response options including, “Never”, “Rarely”, “Often”, “Sometimes”, and “Always”.

Three items were modified the Parental Invasive Behavior subscale of the PPIS to measure student perceptions of invasive behaviors from their teachers. One example item from this subscale is, “My teachers demand that I change my behavior in some area of my life.”

The other 8 modified items came from the Children’s Defensive Behavior subscale, which captured the young adults’ self-reports of behaviors to safeguard their privacy from their teachers. An example of an item from this subscale is, “ I avoid going to see my teacher outside of normal school/class hours. (such as before or after class, during break, before or after school tutoring).”

### Modified Suspicion Scale

Twelve items were adapted from the Suspicion Scale to capture young adults' suspicion toward their teachers. Each item was measured on a seven-point Likert scale, ranging from 0-6, with response options including, "Strongly Disagree", "Somewhat Disagree", "Disagree", "Neither Agree nor Disagree", "Somewhat Agree", "Agree", and "Strongly Agree". Example items from the scale include, "Basically I am a trusting person", and "Most teachers follow the saying "honesty is the best policy."

# Results

# Discussion

# References

### 2023-11-19 scripts/manuscript.qmd
Calculated subscale and total scores, cleaned names, pivoted into tidy format.

@@
 library(psych)
+library(janitor)
 ```
@@
 #| echo: FALSE
-communication <- import(here("data", "communication"))
+communication <- import(here("data", "communication.csv"))
+communication <- (clean_names(communication))
 ```
 
+```{r}
+#| echo: FALSE
+
+#creating the new variables: the ppis subscale 1/parental invasive behaviors score, the ppis subscale 2/student defensive behaviors score, and the suspicion scale score
+comm <- communication %>%
+  mutate(ppis_1_score = rowSums(communication[,5:7])) %>%
+  mutate(ppis_2_score = rowSums(communication[,8:15])) %>%
+  mutate(ss_score = rowSums(communication[,16:27]))
+
+comm <- comm %>%
+  mutate(ppis_total = ppis_1_score + ppis_2_score)
+```
+
+```{r}
+#| echo: FALSE
+
+#pivoting the data, also removing unnecessary columns
+communication <- pivot_longer(comm,
+                      cols = ppis_1_1:ss_12,
+                      names_to = "item",
+                      values_to = "score")
+
+communication <- select(communication, -c(2:7))
+```
+
+```{r}
+#for ben to do later: create summarize data frames to create into a table
+```
 # Introduction

### 2023-11-21 scripts/manuscript.qmd
Data Visualizations
 Boxplot by gender

@@
 library(janitor)
+library(ggplot2)
 ```
@@
 ```
+
+#Data Visualizations
+
+```{r boxplot-gender-ppis-1-score, warning=FALSE, echo=FALSE}
+
+ggplot(communication, aes(gender, ppis_1_score, fill=gender)) +
+  geom_boxplot() +
+  theme(legend.position = "none") +
+  labs(x = "Gender",
+       y = "Parental Invasive Behaviors Score",
+       title = "Boxplot of Parental Invasive Behaviors Score by Gender")
+
+```
+
+```{r boxplot-gender-ppis-2-score, warning=FALSE, echo=FALSE}
+
+ggplot(communication, aes(gender, ppis_2_score, fill=gender)) +
+  geom_boxplot() +
+  theme(legend.position = "none") +
+  labs(x = "Gender",
+       y = "Student Defensive Behaviors Score",
+       title = "Boxplot of Student Defensive Behaviors Score by Gender")
+
+```
+
+```{r boxplot-gender-ppis-total, warning=FALSE, echo=FALSE}
+
+ggplot(communication, aes(gender, ppis_total, fill=gender)) +
+  geom_boxplot() +
+  theme(legend.position = "none") +
+  labs(x = "Gender",
+       y = "Parental Privacy Invasion Scale Total",
+       title = "Boxplot of Parental Privacy Invasion Scale Total by Gender")
+
+```
+
+```{r boxplot-gender-ss-score, warning=FALSE, echo=FALSE}
+
+ggplot(communication, aes(gender, ss_score, fill=gender)) +
+  geom_boxplot() + 
+  theme(legend.position="none") +
+  labs(x = "Gender",
+       y = "Suspicion Scale Score",
+       title = "Boxplot of Suspicion Scale Score by Gender")
+
+```
+
 # Introduction
@@
 
-To measure different aspects of student-teacher trust interactions, items were modified from Ledbetter and Vik’s (2012) Parental Privacy Invasions Scale (PPIS) and Levine and McCornack’s (1991) Suspicion Scale.
+To measure different aspects of student-teacher trust interactions, items were modified from Ledbetter and Vik's (2012) Parental Privacy Invasions Scale (PPIS) and Levine and McCornack's (1991) Suspicion Scale.
 
 ### Modified Parental Privacy Invasions Scale
+
 Eleven items were adapted from the Parental Privacy Invasions Scale to reflect teacher, rather than parental, interactions.
-Each item was measured on a five-point Likert scale, ranging from 0 to 4, with response options including, “Never”, “Rarely”, “Often”, “Sometimes”, and “Always”.
+Each item was measured on a five-point Likert scale, ranging from 0 to 4, with response options including, "Never", "Rarely", "Often", "Sometimes", and "Always".
 
 Three items were modified the Parental Invasive Behavior subscale of the PPIS to measure student perceptions of invasive behaviors from their teachers.
-One example item from this subscale is, “My teachers demand that I change my behavior in some area of my life.”
+One example item from this subscale is, "My teachers demand that I change my behavior in some area of my life."
 
-The other 8 modified items came from the Children’s Defensive Behavior subscale, which captured the young adults’ self-reports of behaviors to safeguard their privacy from their teachers.
-An example of an item from this subscale is, “ I avoid going to see my teacher outside of normal school/class hours.
-(such as before or after class, during break, before or after school tutoring).”
+The other 8 modified items came from the Children's Defensive Behavior subscale, which captured the young adults' self-reports of behaviors to safeguard their privacy from their teachers.
+An example of an item from this subscale is, " I avoid going to see my teacher outside of normal school/class hours.
+(such as before or after class, during break, before or after school tutoring)."
 
@@
 Each item was measured on a seven-point Likert scale, ranging from 0-6, with response options including, "Strongly Disagree", "Somewhat Disagree", "Disagree", "Neither Agree nor Disagree", "Somewhat Agree", "Agree", and "Strongly Agree".
-Example items from the scale include, "Basically I am a trusting person", and "Most teachers follow the saying "honesty is the best policy."
+Example items from the scale include, "Basically I am a trusting person", and "Most teachers follow the saying"honesty is the best policy."
 

### 2023-11-21 scripts/manuscript.qmd
I added the scatterplot!

@@
 
-#Data Visualizations
+# Data Visualizations
 
@@
   theme(legend.position = "none") +
+    scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
   labs(x = "Gender",
-       y = "Parental Invasive Behaviors Score",
-       title = "Boxplot of Parental Invasive Behaviors Score by Gender")
+       y = "Teacher Invasive Behaviors Score",
+       title = "Boxplot of Teacher Invasive Behaviors Score by Gender")
 
@@
   theme(legend.position = "none") +
+  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
   labs(x = "Gender",
@@
   theme(legend.position = "none") +
+    scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
   labs(x = "Gender",
-       y = "Parental Privacy Invasion Scale Total",
-       title = "Boxplot of Parental Privacy Invasion Scale Total by Gender")
+       y = "Teacher Privacy Invasion Scale Total",
+       title = "Boxplot of Teacher Privacy Invasion Scale Total by Gender")
 
@@
   geom_boxplot() + 
+  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
   theme(legend.position="none") +
@@
 
+```
+
+```{r}
+#| label: scatterplot
+#| warning: false
+#| message: false
+#| echo: false
+
+ggplot(comm, aes(ss_score, ppis_total)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  labs(title = "Student's Trustworthiness and Teacher Privacy Invasions", 
+       x = "Own Precieved Trustworthiness",
+       y = "Teacher Privacy Invasions") +
+  theme_minimal()
 ```

### 2023-11-26 scripts/manuscript.qmd
Added a few comments and one small change to labs

@@
 library(ggplot2)
+
+#comment from Frances: I'm not familiar with the psych package - where are you using it?
 ```
@@
        y = "Teacher Invasive Behaviors Score",
-       title = "Boxplot of Teacher Invasive Behaviors Score by Gender")
+       title = "Boxplot of Teacher Invasive Behaviors Score by Gender",
+       subtitle = "Sampled from undergraduate student population in Minnesota, (year?)")
+
+#added a subtitle to indicate age, location, and year of participant survey
 
@@
        title = "Boxplot of Suspicion Scale Score by Gender")
+
+#comment from Frances: I like these boxplots - the data is super clear! You may consider adding a subtitle with a little more information about the study (age, year data was collected, etc.)
 

### 2023-11-29 scripts/manuscript.qmd
Danielle's Peer Review

--- 2023-11-21 scripts/manuscript.qmd
@@
 ---
+```{r}
+# Hi! Danielle here. Your code looks so clean! It is super easy to follow.
+# All of your data and figures loaded properly too. Great job!
+# I have never seen the "scale_x_discrete" code before so I definitely learned that from your code.
+# I really appreciated how you left a note in your code explaining the new labels/why you labeled something the way you did for your collaborators. Super helpful!
+# I noticed that you labeled all the code chunks with box plots so I made a label from your code chunk for the scatter plot following the same format - "scatterplot-ss-score-ppis-total"
+```
 
@@
 
-```{r}
+```{r scatterplot-ss-score-ppis-total}
 #| label: scatterplot

### 2023-11-29 scripts/manuscript.qmd
I started the intro

--- 2023-11-21 scripts/manuscript.qmd
@@
 author: "Leah Peterson, Alexus Rock, and Ben Pfingston"
+bibliography: biblio.bib
 ---
@@
 
+By the time a child turns 18, they have spent approximately 15% of their life at school [@wherry2004].
+Thus, for many young adults, teachers they've encountered are often some of the most influential people in shaping their current knowledge base.
+In addition to influencing student learning and test-scores, supportive teacher communication behaviors have been shown to impact feelings of satisfaction and self-efficacy [@blazar2016; @frymier2000; @chesebro2000].
+Additionally, @Bruney2013 found that teacher relationships are crucial for a young adult's independent thinking skills, which can lead to a greater life satisfaction.
+While childhood is often associated with growth and development, young adulthood is also a time of great advancement in life [@parks2005].
+During this period, young adults are beginning to apply the knowledge they have gained throughout their lives without direct guidance from a parent or authority figure.
+As such, to be successful in this stage of life, young adults need a strong foundation in independent thinking [@Bruney2013].
+In order to build that foundation, experiences of trustful interpersonal relationships with parents, coaches, and teachers are essential in providing support as young adults reconfigure their identities [@parks2005].
+Yet, there is a dearth of research focused on investigating the ways in which overall trust of young adults may be influenced by teachers' communicative behaviors.
+
+## (Dis)Trust & Invasive Behaviors
+
+Trust is a multifaceted concept that encompasses elements such as honesty, connectedness, reliability, and competency [@simpson2007a; @raider-roth2005].
+Further, trust is not an automatic feature in a relationship.
+Caring for and emotional investment in interactions has been shown to be an important factor for building trust [@kuhlmann2008; @smith2005].
+
+Additionally, trust has commonly been viewed as the "glue" that holds together our social order [@rotenberg1995].
+
 (Joe asked us about the specific hypotheses guiding our paper.

### 2023-11-30 scripts/manuscript.qmd
I think the intro is done?
If you want me to add more, just let me know! I also added inline code for the mean age of our participants and filtered out people who didn't provide their age in the comm data. In the results, I added which R packages we're using. If you add a package, can you add the citation too?

@@
 bibliography: biblio.bib
+warning : false
+message : false
+echo : false
 ---
@@
 library(rio)
-library(psych)
 library(janitor)
@@
 comm <- comm %>%
-  mutate(ppis_total = ppis_1_score + ppis_2_score)
+  mutate(ppis_total = ppis_1_score + ppis_2_score,
+         age = as.numeric(age)) %>%  # Convert age column to numeric
+  filter(!is.na(age))
 ```
@@
 
+model <- lm(ppis_total ~ ss_score, comm)
+slope <- coef(model)[2] %>% round(2)
+
 ggplot(comm, aes(ss_score, ppis_total)) +
   geom_point() +
-  geom_smooth(method = "lm") +
+  geom_smooth(method = "lm", color="darkgreen") +
   labs(title = "Student's Trustworthiness and Teacher Privacy Invasions", 
@@
        y = "Teacher Privacy Invasions") +
+   geom_text(x = 30, y = 4,
+     label = sprintf("Slope: %.2f", coef(lm(ppis_total ~ ss_score, data = comm))[2])) +
   theme_minimal()
+
+mean_age <- mean(comm$age) %>% round(2)
+sd_age <- sd(comm$age) %>% round(2)
+
 ```
@@
 As such, to be successful in this stage of life, young adults need a strong foundation in independent thinking [@Bruney2013].
-In order to build that foundation, experiences of trustful interpersonal relationships with parents, coaches, and teachers are essential in providing support as young adults reconfigure their identities [@parks2005].
+In order to build that foundation, experiences of trustful interpersonal relationships with authority figures, such as teachers, are essential in providing support as young adults reconfigure their identities [@parks2005].
 Yet, there is a dearth of research focused on investigating the ways in which overall trust of young adults may be influenced by teachers' communicative behaviors.
@@
 
-Trust is a multifaceted concept that encompasses elements such as honesty, connectedness, reliability, and competency [@simpson2007a; @raider-roth2005].
+Trust is a multifaceted concept that encompasses elements such as honesty, connectedness, reliability, and competency [@simpson2007; @raider-roth2005].
 Further, trust is not an automatic feature in a relationship.
 Caring for and emotional investment in interactions has been shown to be an important factor for building trust [@kuhlmann2008; @smith2005].
+When there is trust in a relationship, commonly individuals act consistently, follow through, and work to meet expectations [@lewicki2006].
+Alternatively, when trust has not been cultivated in a relationship, individuals exhibit greater anti-social behaviors and have impaired psychological adjustment [@simpson2007].
+Additionally, trust in relationships can be broken.
+Specifically, broken trust that is accompanied by invasive behaviors or deception creates the most harm in a relationship and that trust may never fully recover [@schweitzer2006a].
 
-Additionally, trust has commonly been viewed as the "glue" that holds together our social order [@rotenberg1995].
+According to @ledbetter2012, invasive behaviors are those that intend to violate an individual's privacy.
+There are three main categories for invasive behaviors: subversive or spatial invasions, direct or verbal invasions and mediated invasions [@ledbetter2012; @petronio2002].
+Subversive or spatial invasions are acts such as eavesdropping and listening to phone conversations or searching through belongings [@ledbetter2012; @petronio2002].
+Direct or verbal invasions are when something is said directly to the individual who is keeping their information private [@ledbetter2012; @petronio2002].
+Lastly, mediated invasions are when an investigation for information happens through going on someone's social media account, reading emails or text messages or tracking phone activity [@ledbetter2012].
+When trust is broken, individuals commonly are less likely to maintain or create relationships with others in the future, experience anger, become less cooperative in group settings, and give negative evaluations of others [@ledbetter2012; @lount2008; @simpson2007].
+Thus, it is hypothesized that individuals who are more trustworthy will perceive less privacy invasions.
 
-(Joe asked us about the specific hypotheses guiding our paper.
-My suggestion is that we are curious about relations between suspicion and young adults' privacy perceptions, as well as gender differences in young adults suspicion and privacy perceptions)
+## Trust & Gender
+
+Socialization perspectives on gender differences propose that women are more inclined to define themselves in relational terms compared to men [@cross1997].
+This inclination makes women particularly motivated to cultivate positive and nurturing relationships [@cross2000; @amanatullah2008].
+In the context of social relationships, trust has commonly been viewed as the "glue" that holds the relationship together [@rotenberg1995].
+Additionally, following a trust transgression, women are more likely than men to maintain trust in the relationship [@haselhuhn].
+Thus, it is hypothesized that there will be differences in how female, male, and non-binary individuals perceive their own levels of trust towards others, and how they experience privacy invasions.
 
@@
 
-104 participants were recruited primarily through an undergraduate student body located in Minnesota.
-The participation criteria required that participants be at least 18 years old and have interacted with a teacher in a school setting.
-Demographic information, such as age, gender identity, and ethnic-racial identity was also collected.
+98 participants were recruited primarily through an undergraduate student body located in Minnesota.
+The participation criteria required that participants be at least 18 years old (*M =* `r mean_age`, *SD =* `r sd_age`) and have interacted with a teacher in a school setting.
+Demographic information, such as gender identity and ethnic-racial identity, was also collected.
+
+## Procedure
+
+Participants were provided with a link to the survey, which was conducted through the online system Qualtrics.
+Before the survey began, each participant was given an online consent form that provided information about the length of the survey, confidentiality, their ability to withdraw from the study at any time and contact information for the researchers.
 
@@
 
-To measure different aspects of student-teacher trust interactions, items were modified from Ledbetter and Vik's (2012) Parental Privacy Invasions Scale (PPIS) and Levine and McCornack's (1991) Suspicion Scale.
+To measure different aspects of student-teacher trust interactions, items were modified from the @ledbetter2012 Parental Privacy Invasions Scale (PPIS) and the @levine1991 Suspicion Scale.
 
@@
 
+We used R (Version 4.3.2; @R) and the R-packages *ggplot2* [@ggplot], *here* [@here], *janitor* [@janitor], *rio* [@rio], and *tidyverse* [@tidy] for all our analyses.
+
 # Discussion
 
+\newpage
+
 # References

### 2023-12-01 scripts/manuscript.qmd
One code suggestion

--- 2023-11-30 scripts/manuscript.qmd
@@
 #| echo: FALSE
-communication <- import(here("data", "communication.csv"))
-communication <- (clean_names(communication))
+communication <- import(here("data", "communication.csv")) %>% 
+  clean_names()
 ```
+
+Instead of feeding the data into the the `clean_name()` function with another line of code, I suggest piping it directly into `clean_name()`.
+I borrowed this from Dr.Nese's slides and found it convenient.
 

### 2023-12-01 scripts/manuscript.qmd
A big strength I identified

@@
 ```
+
+I appreciate the way you selected using brackets, which made the code cleaner than listing out all options.
+
+One big strength I'd like to learn from your group is that you keep notes (in comments) of what each code chunk is doing.
+This is a good coding habit I have heard before but haven't incorporated into my own practice.
+It'll make revisiting old projects so much easier!
 

### 2023-12-01 scripts/manuscript.qmd
good use of ggplot arguments

@@
 ```
+
+I didn't know that `theme(legend.position = "none")` can omit the legend -- another thing I learned from your group!
+I have looked up  `scale_x_discrete()` before (but am not familiar with its use) and it's cool to see how you set the values for x scale aesthetics.
+
+I also appreciate your naming conventions for each code chunk. This makes code editing and collaboration smoother.
 

### 2023-12-01 scripts/manuscript.qmd
Learned another line of code from this group

@@
 
+Wow impressive specification of your figure here.
+I always struggle with the detailed ggplot arguments to get the vis I want exactly.
+This usually takes a lot of time and digging through code manuals (web pages).
+I commend you!!
+(and saved the ` geom_text(x = 30, y = 4, label = sprintf)...` code for potential future use.)
+
 # Introduction

### 2023-12-02 scripts/manuscript.qmd
Results/description
I will add more to the description / results later if needed

--- 2023-12-01 scripts/manuscript.qmd
@@
 library(ggplot2)
+library(papaja)
 ```
@@
 #| echo: FALSE
-communication <- import(here("data", "communication.csv")) %>% 
-  clean_names()
+communication <- import(here("data", "communication.csv"))
+communication <- (clean_names(communication))
 ```
-
-Instead of feeding the data into the the `clean_name()` function with another line of code, I suggest piping it directly into `clean_name()`.
-I borrowed this from Dr.Nese's slides and found it convenient.
 
@@
 ```
-
-I appreciate the way you selected using brackets, which made the code cleaner than listing out all options.
-
-One big strength I'd like to learn from your group is that you keep notes (in comments) of what each code chunk is doing.
-This is a good coding habit I have heard before but haven't incorporated into my own practice.
-It'll make revisiting old projects so much easier!
 
@@
 model <- lm(ppis_total ~ ss_score, comm)
+modelresults <- apa_print(model)
 slope <- coef(model)[2] %>% round(2)
@@
 
+Privacy invasions and self-rated trustworthiness were not found to be correlated.
+Self-rated trustworthiness was not a significant predictor of privacy invasions (`r modelresults$full_result$ss_score`).
+
+Gender differences existed for teacher invasive behaviors.
+Non-binary individuals perceived their teachers behaviors as being less invasive than females and males perceptions.
+Gender differences existed for teacher privacy invasion.
+Males perceived their teachers invading their privacy less than female and non-binary individuals.
+There were gender differences in the amount of suspicion towards teachers.
+Females had the highest levels of suspicion towards their teachers, and non-binary individuals had the least amount of suspicion.
+
+There were no gender differences in student defensive behaviors.
+
 # Discussion
+
+In this study, self-reported trustworthiness had no influence on perceived privacy invasions.
+Individuals who were more trustworthy did not perceive less privacy invasions than those with less trustworthiness.
+Levels of trustworthiness has no influence on how students perceive their privacy being invaded by teachers.
+
+There were gender differences in how female, male, and non-binary individuals perceived their own levels of trust towards others, and how they experienced privacy invasions.
+Non-binary individuals perceived their teacher's behaviors as being less invasive than female and male individuals.
+Males perceived their teachers invading their privacy less frequently than female and non-binary individuals.
+Females had the highest levels of suspicion towards their teachers, and non-binary individuals had the least amount of suspicion.
+
+There were no gender differences in student defensive behaviors. Students were not more defensive towards their teachers depending on student gender.
 

### 2023-12-05 scripts/manuscript.qmd
Created table, put plots with results, added figure #s to plots.

@@
 library(papaja)
+library(gt)
+library(gtExtras)
 ```
@@
 ```{r}
-#for ben to do later: create summarize data frames to create into a table
-```
-
-# Data Visualizations
-
-```{r boxplot-gender-ppis-1-score, warning=FALSE, echo=FALSE}
-
-ggplot(communication, aes(gender, ppis_1_score, fill=gender)) +
-  geom_boxplot() +
-  theme(legend.position = "none") +
-    scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
-  labs(x = "Gender",
-       y = "Teacher Invasive Behaviors Score",
-       title = "Boxplot of Teacher Invasive Behaviors Score by Gender")
-
-```
-
-```{r boxplot-gender-ppis-2-score, warning=FALSE, echo=FALSE}
-
-ggplot(communication, aes(gender, ppis_2_score, fill=gender)) +
-  geom_boxplot() +
-  theme(legend.position = "none") +
-  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
-  labs(x = "Gender",
-       y = "Student Defensive Behaviors Score",
-       title = "Boxplot of Student Defensive Behaviors Score by Gender")
-
-```
-
-```{r boxplot-gender-ppis-total, warning=FALSE, echo=FALSE}
-
-ggplot(communication, aes(gender, ppis_total, fill=gender)) +
-  geom_boxplot() +
-  theme(legend.position = "none") +
-    scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
-  labs(x = "Gender",
-       y = "Teacher Privacy Invasion Scale Total",
-       title = "Boxplot of Teacher Privacy Invasion Scale Total by Gender")
-
-```
-
-```{r boxplot-gender-ss-score, warning=FALSE, echo=FALSE}
-
-ggplot(communication, aes(gender, ss_score, fill=gender)) +
-  geom_boxplot() + 
-  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
-  theme(legend.position="none") +
-  labs(x = "Gender",
-       y = "Suspicion Scale Score",
-       title = "Boxplot of Suspicion Scale Score by Gender")
-
-```
-
-```{r}
-#| label: scatterplot
-#| warning: false
-#| message: false
-#| echo: false
-
-model <- lm(ppis_total ~ ss_score, comm)
-modelresults <- apa_print(model)
-slope <- coef(model)[2] %>% round(2)
-
-ggplot(comm, aes(ss_score, ppis_total)) +
-  geom_point() +
-  geom_smooth(method = "lm", color="darkgreen") +
-  labs(title = "Student's Trustworthiness and Teacher Privacy Invasions", 
-       x = "Own Precieved Trustworthiness",
-       y = "Teacher Privacy Invasions") +
-   geom_text(x = 30, y = 4,
-     label = sprintf("Slope: %.2f", coef(lm(ppis_total ~ ss_score, data = comm))[2])) +
-  theme_minimal()
-
-mean_age <- mean(comm$age) %>% round(2)
-sd_age <- sd(comm$age) %>% round(2)
-
+ppis_ss_table <- communication %>%
+select(ppis_1_score:ppis_total) %>%
+  pivot_longer(
+  cols = everything(),
+  names_to = "measure",
+  values_to = "score") %>%
+  group_by(measure) %>%
+  summarise(Mean = mean(score, na.rm = TRUE),
+            SD = sd(score, na.rm = TRUE)) %>%
+  pivot_longer(
+    cols = -measure,
+    names_to = "desc",
+    values_to = "value"
+    ) %>%
+  pivot_wider(names_from = measure,
+              values_from = value)
 ```
@@
 
+```{r}
+#| echo: false
+#| warning: fale
+#| message: false
+mean_age <- mean(comm$age) %>% round(2)
+sd_age <- sd(comm$age) %>% round(2)
+```
+
 98 participants were recruited primarily through an undergraduate student body located in Minnesota.
@@
 
-### Modified Parental Privacy Invasions Scale
+### Modified Parental Privacy Invasions Scale: Teacher Privacy Invasions Scale (TPIS)
 
@@
 
-### Modified Suspicion Scale
+### Modified Suspicion Scale (SS)
 
@@
 
+```{r}
+model <- lm(ppis_total ~ ss_score, comm)
+modelresults <- apa_print(model)
+slope <- coef(model)[2] %>% round(2)
+```
+
 We used R (Version 4.3.2; @R) and the R-packages *ggplot2* [@ggplot], *here* [@here], *janitor* [@janitor], *rio* [@rio], and *tidyverse* [@tidy] for all our analyses.
+
+## Descriptive Statistics
+
+The means and standard deviations of the TPIS scores and the SS Scores can be shown in Table 1 below.
+
+```{r}
+#| output: asis
+desc_table <- 
+  gt(ppis_ss_table) %>%
+  cols_label(desc = "Statistic", ppis_1_score = "Teacher Privacy Invasions", ppis_2_score = "Student Trustworthiness", ppis_total = "TPIS Total", ss_score = "Suspicion Scale") %>%
+  tab_caption(caption = "Descriptive Statistics of TPIS and SS Scores ") %>%
+  tab_footnote(footnote = "Table 1.")
+
+desc_table
+```
+
+## Teacher Privacy Invasions and Suspicion Scale
 
@@
 Self-rated trustworthiness was not a significant predictor of privacy invasions (`r modelresults$full_result$ss_score`).
+A scatterplot of the relationship can be seen in Figure 1, shown below.
+
+```{r}
+#| label: scatterplot
+#| warning: false
+#| message: false
+#| echo: false
+
+ggplot(comm, aes(ss_score, ppis_total)) +
+  geom_point() +
+  geom_smooth(method = "lm", color="darkgreen") +
+  labs(title = "Student's Trustworthiness and Teacher Privacy Invasions", 
+       x = "Own Precieved Trustworthiness",
+       y = "Teacher Privacy Invasions",
+       tag = "Figure 1.") +
+   geom_text(x = 30, y = 4,
+     label = sprintf("Slope: %.2f", coef(lm(ppis_total ~ ss_score, data = comm))[2])) +
+  theme_minimal()
+```
+
+## Gender Differences
 
@@
 Males perceived their teachers invading their privacy less than female and non-binary individuals.
+A boxplot of Teacher Invasive Behaviors scores, split by gender, can be found in Figure #.
+There were no gender differences in student defensive behaviors.
+A boxplot of this relationship can be found below in Figure #.
+There were also no differences in the total Teacher Privacy Invasion scale scores between gender groups, shown in the boxplot in Figure #.
+
 There were gender differences in the amount of suspicion towards teachers.
 Females had the highest levels of suspicion towards their teachers, and non-binary individuals had the least amount of suspicion.
+A boxplot of mean Suspicion Scale scores, split by gender, can be found in Figure # below.
 
-There were no gender differences in student defensive behaviors.
+```{r boxplot-gender-ppis-1-score, warning=FALSE, echo=FALSE}
+
+ggplot(communication, aes(gender, ppis_1_score, fill=gender)) +
+  geom_boxplot() +
+  theme(legend.position = "none") +
+    scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
+  labs(x = "Gender",
+       y = "Teacher Invasive Behaviors Score",
+       title = "Boxplot of Teacher Invasive Behaviors Score by Gender", 
+       tag = "Figure 2.")
+```
+
+```{r boxplot-gender-ppis-2-score, warning=FALSE, echo=FALSE}
+
+ggplot(communication, aes(gender, ppis_2_score, fill=gender)) +
+  geom_boxplot() +
+  theme(legend.position = "none") +
+  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
+  labs(x = "Gender",
+       y = "Student Defensive Behaviors Score",
+       title = "Boxplot of Student Defensive Behaviors Score by Gender",
+       tag = "Figure 3.")
+
+```
+
+```{r boxplot-gender-ppis-total, warning=FALSE, echo=FALSE}
+
+ggplot(communication, aes(gender, ppis_total, fill=gender)) +
+  geom_boxplot() +
+  theme(legend.position = "none") +
+    scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
+  labs(x = "Gender",
+       y = "Teacher Privacy Invasion Scale Total",
+       title = "Boxplot of Teacher Privacy Invasion Scale Total by Gender",
+       tag = "Figure 4.")
+
+```
+
+```{r boxplot-gender-ss-score, warning=FALSE, echo=FALSE}
+
+ggplot(communication, aes(gender, ss_score, fill=gender)) +
+  geom_boxplot() + 
+  scale_x_discrete(limits = c("Female", "Male", "Non-binary")) +
+  theme(legend.position="none") +
+  labs(x = "Gender",
+       y = "Suspicion Scale Score",
+       title = "Boxplot of Suspicion Scale Score by Gender",
+       tag = "Figure 5.")
+
+```
 

### 2023-12-06 scripts/manuscript.qmd
Final Touches & Abstract
Added the citations needed, updated figure outputs to be the same theme, added figure #s, and abstract.

@@
 ---
-title: "manuscript"
+title: "EDLD 651 Final Paper"
 format: pdf
@@
   mutate(ppis_total = ppis_1_score + ppis_2_score,
-         age = as.numeric(age)) %>%  # Convert age column to numeric
+         age = as.numeric(age)) %>%  # Converting age column to numeric
   filter(!is.na(age))
@@
   group_by(measure) %>%
-  summarise(Mean = mean(score, na.rm = TRUE),
-            SD = sd(score, na.rm = TRUE)) %>%
+  summarise(Mean = round(mean(score, na.rm = TRUE), 2),
+            SD = round(sd(score, na.rm = TRUE),2)) %>%
   pivot_longer(
@@
 ```
+
+# Abstract
+
+By drawing on theories of gender socialization and trust violations, the current study explores the dynamics of trust and privacy invasions in student-teacher relationships.
+Additionally, this study aims to investigate how gender may impact a young adult's perception of these topics.
+We predict that individuals who are more trustworthy will perceive fewer privacy invasions from teachers in their life.
+A sample of 98 young adults from a Minnesota undergraduate student body participated in this study.
+To measure young adult perceptions of trustworthiness, prior teacher privacy invasions, and suspicion towards teachers, modified scales, including the Parental Privacy Invasions Scale and the Suspicion Scale, were used.
+The results indicate that self-reported trustworthiness does not significantly impact the perception of teacher privacy invasions.
+However, gender differences were observed in how individuals perceive and experience their teacher behaviors.
+This study adds to our understanding of the complex interplay between trust, gender, and privacy invasions in student-teacher relationships.
+Further, the findings emphasize the complexity of trust dynamics in student-teacher relationships and suggest young adults perceive and respond to invasive behaviors in educational settings differently based on their gender identity.
+
+\newpage
 
@@
 ```{r}
-#| echo: false
-#| warning: fale
-#| message: false
 mean_age <- mean(comm$age) %>% round(2)
@@
 
-We used R (Version 4.3.2; @R) and the R-packages *ggplot2* [@ggplot], *here* [@here], *janitor* [@janitor], *rio* [@rio], and *tidyverse* [@tidy] for all our analyses.
+We used R (Version 4.3.2; @R) and the R-packages *ggplot2* [@ggplot], *gt* [@gt], *gtExtras* [@gtE], *here* [@here], *janitor* [@janitor], *papaja* [@papaja], *rio* [@rio], and *tidyverse* [@tidy] for all our analyses.
 
@@
 The means and standard deviations of the TPIS scores and the SS Scores can be shown in Table 1 below.
+
+\newpage
 
@@
 #| label: scatterplot
-#| warning: false
-#| message: false
-#| echo: false
 
@@
 Males perceived their teachers invading their privacy less than female and non-binary individuals.
-A boxplot of Teacher Invasive Behaviors scores, split by gender, can be found in Figure #.
+A boxplot of Teacher Invasive Behaviors scores, split by gender, can be found in Figure 2.
 There were no gender differences in student defensive behaviors.
-A boxplot of this relationship can be found below in Figure #.
-There were also no differences in the total Teacher Privacy Invasion scale scores between gender groups, shown in the boxplot in Figure #.
+A boxplot of this relationship can be found below in Figure 3.
+There were also no differences in the total Teacher Privacy Invasion scale scores between gender groups, shown in the boxplot in Figure 4.
 
@@
 Females had the highest levels of suspicion towards their teachers, and non-binary individuals had the least amount of suspicion.
-A boxplot of mean Suspicion Scale scores, split by gender, can be found in Figure # below.
+A boxplot of mean Suspicion Scale scores, split by gender, can be found in Figure 5 below.
 
-```{r boxplot-gender-ppis-1-score, warning=FALSE, echo=FALSE}
+```{r}
+#| label: boxplot-gender-ppis-1-score
 
@@
        title = "Boxplot of Teacher Invasive Behaviors Score by Gender", 
-       tag = "Figure 2.")
+       tag = "Figure 2.")+
+  theme_minimal()
 ```
 
-```{r boxplot-gender-ppis-2-score, warning=FALSE, echo=FALSE}
-
+```{r}
+#| label: boxplot-gender-ppis-2-score
 ggplot(communication, aes(gender, ppis_2_score, fill=gender)) +
@@
        title = "Boxplot of Student Defensive Behaviors Score by Gender",
-       tag = "Figure 3.")
+       tag = "Figure 3.") +
+  theme_minimal()
 
@@
 
-```{r boxplot-gender-ppis-total, warning=FALSE, echo=FALSE}
+```{r}
+#| label: boxplot-gender-ppis-total
 
@@
        title = "Boxplot of Teacher Privacy Invasion Scale Total by Gender",
-       tag = "Figure 4.")
+       tag = "Figure 4.") +
+  theme_minimal()
 
@@
 
-```{r boxplot-gender-ss-score, warning=FALSE, echo=FALSE}
-
+```{r}
+#| label: boxplot-gender-ss-score
 ggplot(communication, aes(gender, ss_score, fill=gender)) +
@@
        title = "Boxplot of Suspicion Scale Score by Gender",
-       tag = "Figure 5.")
+       tag = "Figure 5.") +
+  theme_minimal()
 
@@
 
-There were no gender differences in student defensive behaviors. Students were not more defensive towards their teachers depending on student gender.
+There were no gender differences in student defensive behaviors. This indicates that students were not more defensive towards their teachers depending on student gender.
 

### 2023-12-06 scripts/manuscript.qmd
Fixed figure width so titles didn't cut off

@@
 #| label: scatterplot
+#| fig-width: 7
 
@@
 #| label: boxplot-gender-ppis-1-score
+#| fig-width: 7
 
@@
 #| label: boxplot-gender-ppis-2-score
+#| fig-width: 7
 ggplot(communication, aes(gender, ppis_2_score, fill=gender)) +
@@
 #| label: boxplot-gender-ppis-total
+#| fig-width: 7
 
@@
 #| label: boxplot-gender-ss-score
+#| fig-width: 7
 ggplot(communication, aes(gender, ss_score, fill=gender)) +
